---
title: "Power Analyses"
author: "Annika Kuelpmann"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup}
#| include: false

knitr::opts_chunk$set(echo = TRUE)

```

### R Packages 
```{r packages}
#| message: false

library(pwrss)
library(pwr)

```

## Power Analyses
All power analyses are performed with the expected sample size of n=120. 

### Correlations (Hypothesis H1)
Hypothesis H1 will be accepted if there is a correlation of at least r=0.7.
```{r power H1}

pwr.r.test(r = 0.7, 
           sig.level = 0.05, 
           n = 120, 
           alternative = "greater")

```

### Correlations (Hypothesis H2)
Hypothesis H1 will be accepted if there is a correlation of at least r=0.6.
```{r power H2}

pwr.r.test(r = 0.6, 
           sig.level = 0.05, 
           n = 120, 
           alternative = "greater")

```

### Correlations (Minimum Effect Size of Interest)
If the above thresholds are not reached, a minimum effect size of interest to detect a positive relationship, even if it does not support the hypotheses H1 and H2, would be r=0.5.
```{r power correlations}

pwr.r.test(r = 0.5, 
           sig.level = 0.05, 
           n = 120, 
           alternative = "greater")

```